---
title: 'p8105_hw5_yl4923'
author: "Yujia Li"
date: "11/19/2021"
output: github_document
---

## Problem 0
--create my public Github repo and local R with a single .Rmd file that renders to github_document
--create a sub-directory to store the local data files used in the assignment, and use relative paths to access these data files
```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)

knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1 
```{r}
# 1.1 Create a city_state variable and describe raw data
homi_df = 
  read_csv("./data/homicide-data.csv",na = c("","Unknown")) %>% 
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )) %>%
  relocate(city_state) %>%
  filter(city_state != "TulsaAL")
```
The homicides data records  `r dim(homi_df)[1]` accidents identified by `r dim(homi_df)[2]` variables in major cities during the past ten years. Key variables include victim characteristics (name, age, sex, etc.), disposition, location (city/state).

The total number of homicides and the number of unsolved homicides within cities are summarized below:
```{r}
homi_stat = 
  homi_df %>% 
  group_by(city_state) %>% 
  summarise(
    unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")), 
    total_number = n()
    )

knitr::kable(homi_stat)
```
